US General Society Survey Analysis

### 2024-03-17 paper/paper.qmd
.
Added subheaders

## Aging and Its Impact on Voting

@@

### Aging Voters (2016)

@@

### Aging Voters (2020)

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

  It is nearly impossible to have data sets that are completely error-free and the same is true for this data set. The data set we used as analysis does not take into account the opinions of non-citizens and who they would have voted for. A lot of marginalized opinions are being left out when we clean the data and we only look for people that could vote. For example, refugees may have a different opinion on who got elected in the 2020 presidential candidate as they come from a different aspect of life and have different priorities that need to be addressed such as housing and or health care. 
  Another weakness in our data set is what occurs with a lot of data sets, which is missing values. This data set also contained them and those needed to be cleaned so that our analysis would not sway. Speaking of missing values, insignificant values were ignored in some of the models as well. For, example some of the presidential candidates got so few votes that including them would have actually hindered our ability to see the trends so we had to group them into others. This was beneficial for this paper but if we do indeed continue to analyze this paper for other purposes, this might cause problems.

>>>>

## The Generational Vote

@@

### The Generational Vote (2016)

@@

### The Generational Vote (2020)

@@

## Dissecting Age Related Demographics

Our exploration into the voting patterns across different age demographics has surfaced intriguing insights into the electoral pulse of America during the 2016 and 2020 presidential elections. In 2016, the expectation was that Hillary Clinton would enjoy robust support from younger voters, yet the data depicted in @fig-hillary2016 revealed a contrary trend: a decrease in support among this demographic. The analysis of the voting trends across the 2016 and 2020 elections has brought to light notable differences in age related voting behaviors, especially concerning Donald Trump's candidacy. In the 2016 election, as depicted by @fig-trump2016, the expectation of a clear trend regarding age and support for Trump was not met. Instead, we observed a mildly chaotic scatter of data points, indicating no strong age-based preference. This was quantitatively supported by a weak positive correlation coefficient, R = 0.12, suggesting that Trump's voter support did not significantly increase or decrease with voters' ages. Alternately, in 2020, the political landscape has shifted with no small part to the global pandemic COVID-19, public discourse and other political movements including but not limited to the death of George Floyd. After many events in Trump's presidency, some within his control and some not, we have the information from @fig-trump2020, where we see more of as pattern among the data points where we can see Trump is more favored among older generations. This suggests an intensification of partisan divides along generational lines, with older voters becoming more entrenched in their support for Trump, while younger voters showed increasing support for the opposing Democratic candidate, Joe Biden.

@@

  It is nearly impossible to have data sets that are completely error-free and the same is true for this data set. The data set we used as analysis does not take into account the opinions of non-citizens and who they would have voted for. A lot of marginalized opinions are being left out when we clean the data and we only look for people that could vote. For example, refugees may have a different opinion on who got elected in the 2020 presidential candidate as they come from a different aspect of life and have different priorities that need to be addressed such as housing and or health care. 
  Another weakness in our data set is what occurs with a lot of data sets, which is missing values. This data set also contained them and those needed to be cleaned so that our analysis would not sway. Speaking of missing values, insignificant values were ignored in some of the models as well. For, example some of the presidential candidates got so few votes that including them would have actually hindered our ability to see the trends so we had to group them into others. This was beneficial for this paper but if we do indeed continue to analyze this paper for other purposes, this might cause problems. 
  Additionally, in the 2016 data there are more candidates that the people voted fore, while not receiving many votes, there were absolutely other candidates mentioned in the 2020 data, as well as no people from the surveyed population chose not to vot unlike in the 2016 election, which could have provided a deeper insight on the differences between the two elections.
